---
title: "Capstone"
author: "Diana Moyano"
date: '2018-11-12'
output: html_document
---

```{r setup, include=FALSE}
#install.packages("knitr")
library(knitr)
knitr::opts_chunk$set(echo = TRUE)

```

Installing and loading packages
```{r, echo=FALSE, include=FALSE }

packages <- c("rmarkdown", "knitr", "plyr","magrittr","tidyverse", "arules", "arulesViz" )
if ( length(missing_pkgs <- setdiff(packages, rownames(installed.packages()))) > 0) {
  message("Installing missing package(s): ", paste(missing_pkgs, collapse = ", "))
  install.packages(missing_pkgs)
}

library(rmarkdown)
library(knitr)
library(magrittr)
library(plyr)
library(arules)
library(arulesViz)
library(tidyverse)

#setwd("/Volumes/Eos/Google Drive/diana_moyano_ovalle/Courses/Git/Capstone_Project")
```


```{r}

RetailF<- read.csv("Association_Rules/Retail_w_Clusters.csv", quote= "\"'", header=T)

RetailF<- RetailF %>% mutate(Date_Order = as.Date(Date_Order, format="%Y-%m-%d")) %>% mutate(CustomerID = factor(CustomerID)) %>% mutate(InvoiceNo = factor(InvoiceNo))

head(RetailF)
```
Below is an example of the data preparation for the whole dataset. The same process will be performed on each cluster.

.	The dataset is rearranged in a way that all transactions with the same Invoice number and date will be grouped. All the products will be also grouped in one column, separated by a comma (this chunk will take a while to produce an output)
```{r}

Whole <- ddply(RetailF,c("InvoiceNo","Date_Order"),
                       function(RetailF)paste(RetailF$Description,
                       collapse = ","))
head(Whole)

```

.	The InvoiceNo and the Date_Order are removed
.	The remaining column is renamed "Products"
.	The new dataset is saved as a csv file
```{r}
#set column InvoiceNo of dataframe Whole  
Whole$InvoiceNo <- NULL
#set column Date_Order of dataframe Whole
Whole$Date_Order <- NULL
#Rename column to Products
colnames(Whole) <- c("Products")

head(Whole)


write.csv(Whole,"Association_Rules/Whole.csv", quote = FALSE, row.names = FALSE)

```
The same procedure is done for all cluster groups (we just need to subset them first).

*_This chunk will take some minutes to process and won't produce any output. Instead, it will create a csv file per cluster group so they can be used in the next section (_04_AR_Selection.Rmd)_*

```{r}

##4 CLUSTERS
###Kmeans

#Group 1
K4cl_g1<-subset(RetailF,RetailF$k4==1)

K4cl_g1T <- ddply(K4cl_g1,c("InvoiceNo","Date_Order"),
                       function(K4cl_g1)paste(K4cl_g1$Description,
                       collapse = ","))

K4cl_g1T$InvoiceNo<- NULL
K4cl_g1T$Date_Order<-NULL

colnames(K4cl_g1T)<- "Products"

write.csv(K4cl_g1T,"Association_Rules/K4cl_g1T.csv", quote = FALSE, row.names = FALSE)



#Group 2
K4cl_g2<-subset(RetailF,RetailF$k4==2)

K4cl_g2T <- ddply(K4cl_g2,c("InvoiceNo","Date_Order"),
                       function(K4cl_g2)paste(K4cl_g2$Description,
                       collapse = ","))

K4cl_g2T$InvoiceNo<- NULL
K4cl_g2T$Date_Order<-NULL

colnames(K4cl_g2T)<- "Products"

write.csv(K4cl_g2T,"Association_Rules/K4cl_g2T.csv", quote = FALSE, row.names = FALSE)

#Group 3
K4cl_g3<-subset(RetailF,RetailF$k4==3)

K4cl_g3T <- ddply(K4cl_g3,c("InvoiceNo","Date_Order"),
                       function(K4cl_g3)paste(K4cl_g3$Description,
                       collapse = ","))

K4cl_g3T$InvoiceNo<- NULL
K4cl_g3T$Date_Order<-NULL

colnames(K4cl_g3T)<- "Products"

write.csv(K4cl_g3T,"Association_Rules/K4cl_g3T.csv", quote = FALSE, row.names = FALSE)

#Group 4
K4cl_g4<-subset(RetailF,RetailF$k4==4)

K4cl_g4T <- ddply(K4cl_g4,c("InvoiceNo","Date_Order"),
                       function(K4cl_g4)paste(K4cl_g4$Description,
                       collapse = ","))

K4cl_g4T$InvoiceNo<- NULL
K4cl_g4T$Date_Order<-NULL

colnames(K4cl_g4T)<- "Products"

write.csv(K4cl_g4T,"Association_Rules/K4cl_g4T.csv", quote = FALSE, row.names = FALSE)


##4 CLUSTERS
### PAM Euclidean

#Group 1
PE4cl_g1<-subset(RetailF,RetailF$pe4==1)

PE4cl_g1T <- ddply(PE4cl_g1,c("InvoiceNo","Date_Order"),
                       function(PE4cl_g1)paste(PE4cl_g1$Description,
                       collapse = ","))

PE4cl_g1T$InvoiceNo<- NULL
PE4cl_g1T$Date_Order<-NULL

colnames(PE4cl_g1T)<- "Products"

write.csv(PE4cl_g1T,"Association_Rules/PE4cl_g1T.csv", quote = FALSE, row.names = FALSE)


#Group 2
PE4cl_g2<-subset(RetailF,RetailF$pe4==2)

PE4cl_g2T <- ddply(PE4cl_g2,c("InvoiceNo","Date_Order"),
                       function(PE4cl_g2)paste(PE4cl_g2$Description,
                       collapse = ","))

PE4cl_g2T$InvoiceNo<- NULL
PE4cl_g2T$Date_Order<-NULL

colnames(PE4cl_g2T)<- "Products"

write.csv(PE4cl_g2T,"Association_Rules/PE4cl_g2T.csv", quote = FALSE, row.names = FALSE)


#Group 3
PE4cl_g3<-subset(RetailF,RetailF$pe4==3)

PE4cl_g3T <- ddply(PE4cl_g3,c("InvoiceNo","Date_Order"),
                       function(PE4cl_g3)paste(PE4cl_g3$Description,
                       collapse = ","))

PE4cl_g3T$InvoiceNo<- NULL
PE4cl_g3T$Date_Order<-NULL

colnames(PE4cl_g3T)<- "Products"

write.csv(PE4cl_g3T,"Association_Rules/PE4cl_g3T.csv", quote = FALSE, row.names = FALSE)



#Group 4
PE4cl_g4<-subset(RetailF,RetailF$pe4==4)

PE4cl_g4T <- ddply(PE4cl_g4,c("InvoiceNo","Date_Order"),
                       function(PE4cl_g4)paste(PE4cl_g4$Description,
                       collapse = ","))

PE4cl_g4T$InvoiceNo<- NULL
PE4cl_g4T$Date_Order<-NULL

colnames(PE4cl_g4T)<- "Products"

write.csv(PE4cl_g4T,"Association_Rules/PE4cl_g4T.csv", quote = FALSE, row.names = FALSE)


##4 CLUSTERS
### PAM Manhattan


#Group 1
PM4cl_g1<-subset(RetailF,RetailF$pm4==1)

PM4cl_g1T <- ddply(PM4cl_g1,c("InvoiceNo","Date_Order"),
                       function(PM4cl_g1)paste(PM4cl_g1$Description,
                       collapse = ","))

PM4cl_g1T$InvoiceNo<- NULL
PM4cl_g1T$Date_Order<-NULL

colnames(PM4cl_g1T)<- "Products"

write.csv(PM4cl_g1T,"Association_Rules/PM4cl_g1T.csv", quote = FALSE, row.names = FALSE)



#Group 2
PM4cl_g2<-subset(RetailF,RetailF$pm4==2)

PM4cl_g2T <- ddply(PM4cl_g2,c("InvoiceNo","Date_Order"),
                       function(PM4cl_g2)paste(PM4cl_g2$Description,
                       collapse = ","))

PM4cl_g2T$InvoiceNo<- NULL
PM4cl_g2T$Date_Order<-NULL

colnames(PM4cl_g2T)<- "Products"

write.csv(PM4cl_g2T,"Association_Rules/PM4cl_g2T.csv", quote = FALSE, row.names = FALSE)


#Group 3
PM4cl_g3<-subset(RetailF,RetailF$pm4==3)

PM4cl_g3T <- ddply(PM4cl_g3,c("InvoiceNo","Date_Order"),
                       function(PM4cl_g3)paste(PM4cl_g3$Description,
                       collapse = ","))

PM4cl_g3T$InvoiceNo<- NULL
PM4cl_g3T$Date_Order<-NULL

colnames(PM4cl_g3T)<- "Products"

write.csv(PM4cl_g3T,"Association_Rules/PM4cl_g3T.csv", quote = FALSE, row.names = FALSE)


#Group 4
PM4cl_g4<-subset(RetailF,RetailF$pm4==4)

PM4cl_g4T <- ddply(PM4cl_g4,c("InvoiceNo","Date_Order"),
                       function(PM4cl_g4)paste(PM4cl_g4$Description,
                       collapse = ","))

PM4cl_g4T$InvoiceNo<- NULL
PM4cl_g4T$Date_Order<-NULL

colnames(PM4cl_g4T)<- "Products"

write.csv(PM4cl_g4T,"Association_Rules/PM4cl_g4T.csv", quote = FALSE, row.names = FALSE)


## 5 CLUSTERS
###K-means

#Group 1
K5cl_g1<-subset(RetailF,RetailF$k5==1)

K5cl_g1T <- ddply(K5cl_g1,c("InvoiceNo","Date_Order"),
                       function(K5cl_g1)paste(K5cl_g1$Description,
                       collapse = ","))

K5cl_g1T$InvoiceNo<- NULL
K5cl_g1T$Date_Order<-NULL

colnames(K5cl_g1T)<- "Products"

write.csv(K5cl_g1T,"Association_Rules/K5cl_g1T.csv", quote = FALSE, row.names = FALSE)



#Group 2
K5cl_g2<-subset(RetailF,RetailF$k5==2)

K5cl_g2T <- ddply(K5cl_g2,c("InvoiceNo","Date_Order"),
                       function(K5cl_g2)paste(K5cl_g2$Description,
                       collapse = ","))

K5cl_g2T$InvoiceNo<- NULL
K5cl_g2T$Date_Order<-NULL

colnames(K5cl_g2T)<- "Products"

write.csv(K5cl_g2T,"Association_Rules/K5cl_g2T.csv", quote = FALSE, row.names = FALSE)


#Group 3
K5cl_g3<-subset(RetailF,RetailF$k5==3)

K5cl_g3T <- ddply(K5cl_g3,c("InvoiceNo","Date_Order"),
                       function(K5cl_g3)paste(K5cl_g3$Description,
                       collapse = ","))

K5cl_g3T$InvoiceNo<- NULL
K5cl_g3T$Date_Order<-NULL

colnames(K5cl_g3T)<- "Products"

write.csv(K5cl_g3T,"Association_Rules/K5cl_g3T.csv", quote = FALSE, row.names = FALSE)


#Group 4
K5cl_g4<-subset(RetailF,RetailF$k5==4)

K5cl_g4T <- ddply(K5cl_g4,c("InvoiceNo","Date_Order"),
                       function(K5cl_g4)paste(K5cl_g4$Description,
                       collapse = ","))

K5cl_g4T$InvoiceNo<- NULL
K5cl_g4T$Date_Order<-NULL

colnames(K5cl_g4T)<- "Products"

write.csv(K5cl_g4T,"Association_Rules/K5cl_g4T.csv", quote = FALSE, row.names = FALSE)



#Group 5
K5cl_g5<-subset(RetailF,RetailF$k5==5)

K5cl_g5T <- ddply(K5cl_g5,c("InvoiceNo","Date_Order"),
                       function(K5cl_g5)paste(K5cl_g5$Description,
                       collapse = ","))

K5cl_g5T$InvoiceNo<- NULL
K5cl_g5T$Date_Order<-NULL

colnames(K5cl_g5T)<- "Products"

write.csv(K5cl_g5T,"Association_Rules/K5cl_g5T.csv", quote = FALSE, row.names = FALSE)

##5 CLUSTERS
###PAM - Euclidean

#Group 1
PE5cl_g1<-subset(RetailF,RetailF$pe5==1)

PE5cl_g1T <- ddply(PE5cl_g1,c("InvoiceNo","Date_Order"),
                       function(PE5cl_g1)paste(PE5cl_g1$Description,
                       collapse = ","))

PE5cl_g1T$InvoiceNo<- NULL
PE5cl_g1T$Date_Order<-NULL

colnames(PE5cl_g1T)<- "Products"

write.csv(PE5cl_g1T,"Association_Rules/PE5cl_g1T.csv", quote = FALSE, row.names = FALSE)



#Group 2
PE5cl_g2<-subset(RetailF,RetailF$pe5==2)

PE5cl_g2T <- ddply(PE5cl_g2,c("InvoiceNo","Date_Order"),
                       function(PE5cl_g2)paste(PE5cl_g2$Description,
                       collapse = ","))

PE5cl_g2T$InvoiceNo<- NULL
PE5cl_g2T$Date_Order<-NULL

colnames(PE5cl_g2T)<- "Products"

write.csv(PE5cl_g2T,"Association_Rules/PE5cl_g2T.csv", quote = FALSE, row.names = FALSE)



#Group 3
PE5cl_g3<-subset(RetailF,RetailF$pe5==3)

PE5cl_g3T <- ddply(PE5cl_g3,c("InvoiceNo","Date_Order"),
                       function(PE5cl_g3)paste(PE5cl_g3$Description,
                       collapse = ","))

PE5cl_g3T$InvoiceNo<- NULL
PE5cl_g3T$Date_Order<-NULL

colnames(PE5cl_g3T)<- "Products"

write.csv(PE5cl_g3T,"Association_Rules/PE5cl_g3T.csv", quote = FALSE, row.names = FALSE)



#Group 4
PE5cl_g4<-subset(RetailF,RetailF$pe5==4)

PE5cl_g4T <- ddply(PE5cl_g4,c("InvoiceNo","Date_Order"),
                       function(PE5cl_g4)paste(PE5cl_g4$Description,
                       collapse = ","))

PE5cl_g4T$InvoiceNo<- NULL
PE5cl_g4T$Date_Order<-NULL

colnames(PE5cl_g4T)<- "Products"

write.csv(PE5cl_g4T,"Association_Rules/PE5cl_g4T.csv", quote = FALSE, row.names = FALSE)



#Group 5
PE5cl_g5<-subset(RetailF,RetailF$pe5==5)

PE5cl_g5T <- ddply(PE5cl_g5,c("InvoiceNo","Date_Order"),
                       function(PE5cl_g5)paste(PE5cl_g5$Description,
                       collapse = ","))

PE5cl_g5T$InvoiceNo<- NULL
PE5cl_g5T$Date_Order<-NULL

colnames(PE5cl_g5T)<- "Products"

write.csv(PE5cl_g5T,"Association_Rules/PE5cl_g5T.csv", quote = FALSE, row.names = FALSE)

##5 CLUSTERS
###PAM - Manhattan

#Group 1
PM5cl_g1<-subset(RetailF,RetailF$pm5==1)

PM5cl_g1T <- ddply(PM5cl_g1,c("InvoiceNo","Date_Order"),
                       function(PM5cl_g1)paste(PM5cl_g1$Description,
                       collapse = ","))

PM5cl_g1T$InvoiceNo<- NULL
PM5cl_g1T$Date_Order<-NULL

colnames(PM5cl_g1T)<- "Products"

write.csv(PM5cl_g1T,"Association_Rules/PM5cl_g1T.csv", quote = FALSE, row.names = FALSE)


#Group 2
PM5cl_g2<-subset(RetailF,RetailF$pm5==2)

PM5cl_g2T <- ddply(PM5cl_g2,c("InvoiceNo","Date_Order"),
                       function(PM5cl_g2)paste(PM5cl_g2$Description,
                       collapse = ","))

PM5cl_g2T$InvoiceNo<- NULL
PM5cl_g2T$Date_Order<-NULL

colnames(PM5cl_g2T)<- "Products"

write.csv(PM5cl_g2T,"Association_Rules/PM5cl_g2T.csv", quote = FALSE, row.names = FALSE)


#Group 3
PM5cl_g3<-subset(RetailF,RetailF$pm5==3)

PM5cl_g3T <- ddply(PM5cl_g3,c("InvoiceNo","Date_Order"),
                       function(PM5cl_g3)paste(PM5cl_g3$Description,
                       collapse = ","))

PM5cl_g3T$InvoiceNo<- NULL
PM5cl_g3T$Date_Order<-NULL

colnames(PM5cl_g3T)<- "Products"

write.csv(PM5cl_g3T,"Association_Rules/PM5cl_g3T.csv", quote = FALSE, row.names = FALSE)


#Group 4
PM5cl_g4<-subset(RetailF,RetailF$pm5==4)

PM5cl_g4T <- ddply(PM5cl_g4,c("InvoiceNo","Date_Order"),
                       function(PM5cl_g4)paste(PM5cl_g4$Description,
                       collapse = ","))

PM5cl_g4T$InvoiceNo<- NULL
PM5cl_g4T$Date_Order<-NULL

colnames(PM5cl_g4T)<- "Products"

write.csv(PM5cl_g4T,"Association_Rules/PM5cl_g4T.csv", quote = FALSE, row.names = FALSE)



#Group 5
PM5cl_g5<-subset(RetailF,RetailF$pm5==5)

PM5cl_g5T <- ddply(PM5cl_g5,c("InvoiceNo","Date_Order"),
                       function(PM5cl_g5)paste(PM5cl_g5$Description,
                       collapse = ","))

PM5cl_g5T$InvoiceNo<- NULL
PM5cl_g5T$Date_Order<-NULL

colnames(PM5cl_g5T)<- "Products"

write.csv(PM5cl_g5T,"Association_Rules/PM5cl_g5T.csv", quote = FALSE, row.names = FALSE)

```
